Ice sheet mass flows

### 2024-06-24 ms.tex
Basal melt in AQ. Closes #14

Most existing estimates are provided with enough geospatial metadata that we simply assign flow estimates to the appropriate region. However, we do not have access to the basal mass balance for Antarctica in spatial map form, only a total Antarctic-wide value from \citet{pattyn_2010} reported at 65 Gt yr$^{-1}$. To estimate basal melt for East and West Antarctica, we scale by the magnitude of geothermal heat flux (from \citet{shapiro_2004}) scaled by area for East, West, and Peninsula which is 70 \%, 25 \%, and 5 \% respectively. This is slightly better than scaling by area alone which has 75 \% of the area in East Antarctica. This method neglects the contribution of shear heating (ice velocity) when partitioning basal melt.

@@

\begin{table*}
\caption{Mass flow values used for Antarctica and Antarctica regions in Fig. \ref{fig}}
\label{tab:aq}
\begin{tabular}{@{}lcc}\hline
  Term & Source\\
  Snowfall & \citet{fettweis_2020}\\
  Rainfall & \citet{fettweis_2020}\\
  Condensation & TODO\\
  Deposition & TODO\\
  Sublimation & \citet{fettweis_2020}\\
  Evaporation & \citet{fettweis_2020}\\
  Runoff & \citet{fettweis_2020}\\
  Refreezing & \citet{fettweis_2020}\\
  Frontal retreat & TODO\\
  Grounding line retreat & TODO\\
  Discharge + submarine melting & \citet{davison_2023}\\
  Split of discharge \& submarine melting & \citet{davison_2023}\\
  Basal melting & \citet{pattyn_2010}\\
  Regional distribution terms & See Sect. \ref{sec:methods:split}\\
  Drawdown or accumulation & Derived from above
\end{tabular}
\end{table*}

>>>>

@@

\begin{table*}
\caption{Mass flow values used for Antarctica and Antarctica regions in Fig. \ref{fig}}
\label{tab:aq}
\begin{tabular}{@{}lcc}\hline
  Term & Source\\
  Snowfall & \citet{fettweis_2020}\\
  Rainfall & \citet{fettweis_2020}\\
  Condensation & TODO\\
  Deposition & TODO\\
  Sublimation & \citet{fettweis_2020}\\
  Evaporation & \citet{fettweis_2020}\\
  Runoff & \citet{fettweis_2020}\\
  Refreezing & \citet{fettweis_2020}\\
  Frontal retreat & TODO\\
  Grounding line retreat & TODO\\
  Discharge + submarine melting & \citet{davison_2023}\\
  Split of discharge \& submarine melting & \citet{davison_2023}\\
  Basal melting & \citet{van-liefferinge_2013}\\
  Drawdown or accumulation & Derived from above
\end{tabular}
\end{table*}
